Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-30 Paper/related.tex
Jed made some minor edits

taken in this paper. First, the authors in \cite{throats} didn't consider that

@@

to include more nations. Additionally, this study didn't include the United States and Russia in their experiments because they were

>>>>

taken in this paper. First, the authors in \cite{throats} did not consider that

@@

to include more nations. Additionally, this study did not include the United States and Russia in their experiments because they were
